---
title: "Activity 1.2 - RStudio and R Markdown"
author: "Stephen Bennett"
date: "8/29/2019"
output: 
  html_document: 
    fig_height: 8
    fig_width: 8
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

Based on the help file, there are 1846 rows and 3 columns in the datasaurus_dozen file. The variables included in the data frame are "dataset", "x", and "y".

### Exercise 2

(The answers for this Exercise are given for you below. But you should clean up some of the narrative so that it only includes what you want to turn in.)

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```
The correlation coefficient for the dino data is r = -0.0645. This shows that there is a very weak negative relationship between x and y, so when x increases, y tends to decrease. Although again, this represents a very weaks relationship and shows that the two variables are hardly related at all.

### Exercise 3

The correlation coefficient for the star data is r = -0.0630. This shows that there is a very weak negative relationship between x and y, so when x increases, y tends to decrease. Although again, this represents a very weaks relationship and shows that the two variables are hardly related at all. Compared with the correlation of the dino data set, this set has a slightly weaker linear relationship than that of the dino data although both are close to having no relationship whatsoever.

Code to plot the data from the star data set
```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Here is code to find the correlation coefficient from the star data set.

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```

### Exercise 4

The correlation coefficient for the circle data is r = -0.0683. This shows that there is a very weak negative relationship between x and y, so when x increases, y tends to decrease. This represents a very weaks relationship and shows that the two variables are hardly related at all. Compared with the correlation of the dino data set, this set has a slightly stronger linear relationship than that of the dino data although both are close to having no relationship whatsoever.

Code to plot the data from the star data set
```{r}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")

ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Here is code to find the correlation coefficient from the circle data set.
```{r}
circle_data %>%
  summarize(r = cor(x, y))
```

### Exercise 5

Code using faceting to display all dataset plots at once.
```{r}
ggplot(data = datasaurus_dozen, aes(x = x, y = y, color = dataset)) + geom_point() + facet_wrap(~ dataset, ncol = 3) + theme(legend.position = "none")
```

Code to display all correlation coefficients at once.
```{r}
datasaurus_dozen %>%
  group_by(dataset)
  summarize(r = cor(x, y))
  print(13)
```

The use of faceting to find all the correlations at once provided us with the following output, giving us the name of the dataset and its respective x and y correlation:
 1 away       -0.0641
 2 bullseye   -0.0686
 3 circle     -0.0683
 4 dino       -0.0645
 5 dots       -0.0603
 6 h_lines    -0.0617
 7 high_lines -0.0685
 8 slant_down -0.0690
 9 slant_up   -0.0686
10 star       -0.0630
11 v_lines    -0.0694
12 wide_lines -0.0666
13 x_shape    -0.0656

We can see here that all correlation values are between -0.060 and -0.070, meaning that these datasets all have correlations that show an extremely weak negative linear relationship between x and y. The dataset "v_lines" has the strongest relationship, while the dataset "dots" has the weakest relationship. None of these datasets shows anything close to a significant linear relationship.